Predicting tree failure likelihood for utility risk mitigation via a novel convolutional neural network

### 2021-02-18 docs/manuscript/manuscript.tex
formatted hyperparameter table
Updates from Overleaf

@@

     % \begin{tabular}{l  c  p{1.75cm} p{1.75cm}  p{1.75cm} p{1.75cm}}\toprule
    % \bf Scenario & \bf Hyperparameter & \multicolumn{3}{c}{\bf Resolution ($n\times n$ pixels)} \\
    % &         & 64 & 128 & 224   \\\midrule
    % \multirow{7}{*}{\texttt{Pr\_Po\_Im}} 
    %     & $ks$    & 7 &  &     \\
    %     & $u_1$   & 128 &  &     \\
    %     & $d_1$   & 0.25 &  &     \\
    %     & $a_1$   & ReLu  &  &      \\
    %     & $u_2$   & 320 &  &    \\
    %     & $d_2$   & 0.30 &  &     \\
    %     & $a_2$   & ReLu &  &     \\
    %     & $\lambda$  & $1.76\cdot 10^{-4}$ &  &      \\ \midrule
    % \multirow{7}{*}{\texttt{Pr\_Im}} 
    %     & $ks$    & 7 &  &      \\
    %     & $u_1$   & 128 &  &     \\
    %     & $d_1$   & 0.25 &  &      \\
    %     & $a_1$   & ReLu  &  &      \\
    %     & $u_2$   & 320 &  &      \\
    %     & $d_2$   & 0.30 &  &     \\
    %     & $a_2$   & ReLu &  &      \\
    %     & $\lambda$  & $1.76\cdot 10^{-4}$ &  &      \\ \midrule
    % \multirow{7}{*}{\texttt{PrPo\_Im}} 
    %     & $ks$    & 7 &  &    \\
    %     & $u_1$   & 128 &  &     \\
    %     & $d_1$   & 0.25 &  &      \\
    %     & $a_1$   & ReLu  &  &     \\
    %     & $u_2$   & 320 &  &     \\
    %     & $d_2$   & 0.30 &  &     \\
    %     & $a_2$   & ReLu &  &      \\
    %     & $\lambda$  & $1.76\cdot 10^{-4}$ &  &     \\ \midrule
    % \multirow{7}{*}{\texttt{Pr\_PoIm}}  
    %     & $ks$    & 7 &  &      \\
    %     & $u_1$   & 128 &  &      \\
    %     & $d_1$   & 0.25 &  &      \\
    %     & $a_1$   & ReLu  &  &      \\
    %     & $u_2$   & 320 &  &      \\
    %     & $d_2$   & 0.30 &  &     \\
    %     & $a_2$   & ReLu &  &      \\
    %     & $\lambda$  & $1.76\cdot 10^{-4}$ &  &  &   \\ \bottomrule
    % \end{tabular}

>>>>

The structure of the CNN is shown in \autoref{fig:cnn}.

\begin{figure}
    \centering
    \includegraphics[width=.9\textwidth]{net2vis/graph.pdf}

    \medskip

    \includegraphics[width=.7\textwidth]{figures/net2vis-name-labels/legend}
    \caption{Diagram of convolutional neural network structure. Hyperparameters that are optimized include the number of units in the penultimate dense layers. (Generated using automated framework \cite{bauerle2021net2vis})}
    \label{fig:cnn}
\end{figure}

@@

% Table edited at: https://www.tablesgenerator.com/latex_tables#
